Black hole symphony orchestra: Spectroscopy using gravitational wave signals from binary black hole coalescences

### 2020-12-02 papers/intro_paper/intro_paper.tex

\title{Black hole symphony orchestra: Spectroscopy using gravitational wave signals from binary black holes}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The no-hair conjecture in General Relativity states that the properties of a Kerr black hole (BH) are completely described by its mass and spin angular momentum. As a consequence, the complex quasi-normal-mode (QNM) frequencies of a binary black hole (BBH) ringdown can be uniquely determined by the mass and spin of the remnant object. Conversely, measurement of the QNM frequencies could be a independent test of the no-hair conjecture. This paper outlines a test of the no-hair conjecture by measuring the complex QNM frequencies of a BBH ringdown within the framework of, for the first time, a spinning inspiral-merger-ringdown waveform model, thereby using the entire signal power and removing dependency on the predicted or estimated start time of the proposed ringdown. We further demonstrate the robustness of the test against modified gravitational wave (GW) signals with a ringdown different from what GR predicts for Kerr BHs. The method was used to analyse the properties of the merger remnants for the events observed by LIGO-Virgo in the first half of their third observing run (O3a) in the latest LIGO-Virgo publication. In this paper, for the first time, we analyse the GW events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a. Finally, the joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest constraints yet using this method. %Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, we provide a simple demonstration of a test of the no-hair theorem using our model. As described in the introduction, any test of the no-hair theorem of BHs would need to involve independent measurements of (at least) two different QNMs. We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning BBH with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$. We choose an asymmetric system to increase the SNR in the higher modes. We also rescale the distance and orientation of the binary such that the total SNR of the signal in a network of three detectors, LIGO Hanford, Livingston and Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such asymmetric and loud signals are no longer just a theoretical prediction but quite plausible at design sensitivities. Using this signal, we attempt to measure the QNM frequencies $(2,\pm 2)$ and $(3,\pm 3)$ modes together (Fig.~\ref{fig:nohair_sxs}). The SNR in other sub-dominant modes is too less for us to estimate them reliably.

@@

The LIGO-Virgo Collaboration recently released their testing GR catalogue containing results of this test for all events observed during the first half of O3 CITE, which passed a threshold for the total detector frame mass $\geq 50 \Mo$ and SNRs in the pre- and post-merger regions $\geq 8$.The pre- and post-merger regions of the signal are identified as the power in the frequency content of the signal before and after the signal reaches peak amplitude, as determined by the maximum likelihood parameter estimation template. We restricted ourselves to the high-mass events which are expected to be merger-ringdown dominated. However, since our method relies on doing a parameter estimation on the entire inspiral-merger-ringdown signal, we require the SNR to be beyond a certain threshold throughout the signal for reliable parameter estimation of the initial and final quantities. Fig.~\ref{fig:o1o2_events} contains three events from O3a, GW190519\_ 153544, GW190521\_ 074359, GW190910\_ 112807.

For the first time, in this paper, we present results on the relevant events from LIGO-Virgo's first and second observing runs, alongside the above events. Applying the same thresholds as above, we find three additional events which could be included in the analysis: GW150914, GW170104, GW170729 \abhi{would need to confirm the thresholds again, and see if GW170809 qualifies}. Regarding the other two high-mass events, GW170814 and GW170823 do not satisfy the SNR thresholds. For the three relevant signals, GW150914, GW170104 and GW170729, we provide the posterior distributions in $(\df{220}, \dtau{220})$ in Fig.\ref{fig:o1o2_events}. We also reconstruct the effective QNM parameters, $(\fngr{220}, \taungr{220})$ which are tabulated in Table~\ref{tab:qnm_o1o2_results}.

Among all the GW signals detected so far, GW150914 is unique in its loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.  Fig.\ref{fig:GW150914_real} compares the results we obtain for GW150914 using $\pSEOB$ with previously published LIGO-Virgo results using a damped-sinusoid method, as well as the measurement reported using a non-spinning model in \paperone. The damped-sinusoid model assumed specific cutoff times (indicated in the curves on the bottom panel of Fig.\ref{fig:o1o2_events}) after the time corresponding to the peak amplitude as predicted by the best-fitting GR template waveform. Increasing time, decreasing SNR, wider posteriors, less-precise measurement. Compared to that we see when we incorporate the complete IMR version of the test, we utilise more SNR leading to tighter constraints.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% O1-O2 events
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
	\includegraphics[width=0.5\textwidth]{figures/O1O2_realevents.pdf}
	\caption{\textcolor{red}{FINAL RESULT}The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions. We also plot the joint probability distribution obtained by multiplying the likelihoods of the $\{\df{220},\dtau{220}\}$ (black dashed line) \abhi{need to compute the joint likelihood. currently contains the hierarchical contour from the O3a TGR paper}}
	\label{fig:o1o2_events}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalised distributions as black dashed lines in Fig.~\ref{fig:o1o2_events}. These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method. \abhi{perhaps show 2 joint posteriors: only O3a and O3a+O1-O2 to explicitly show the tightening of the joint constraints by adding the O1-O2 events}

\begin{table}
\begin{center}
\begin{tabular}{llllllll}
\toprule
Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
\cline{2-4}
\cline{6-8}
& IMR  & pSEOB & \hphantom{X} & IMR  & pSEOB \\
\midrule

@@

\bottomrule
\end{tabular}
\caption{\textcolor{red}{NOT COMPLETE}}
\label{tab:qnm_o1o2_results}
\end{center}
\end{table}

@@

In Section~\ref{sec:method}, we mentioned that the expression of the Bayesian likelihood function outlined in Eqs.~\ref{eq:likelihood} and \ref{eq:nwip} is only valid if the interferometric noise can be described as a stationary Gaussian process. LIGO-Virgo noise, however, frequently has non-stationary and/or non-Gaussian features, like glitches, PSD drift, etc, which can affect parameter inferences unless appropriately accounted for.

Here we demonstrate with an example, systematic biases likely originating from an incomplete understanding of the noise using the example of the GW190521. In Fig.~\ref{ig:o1o2_events} \abhi{include GW190521A in figure}, we find the estimates of the fractional deviations in the damping time, $\dtau{220}$ does not enclose the GR prediction at the 90 \% credible level, although the fractional deviation in the frequency $\df{220}$ is.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
	\caption{\textcolor{red}{FINAL RESULT}90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220}$ from simulations of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines). The GR prediction for the frequency and damping time is indicated by the black cross. While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not. For comparison, we also plot the 90 \% credible level for the actual event, GW190521.}
	\label{fig:21g_systematics}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We injected NRSur7dq4 signal using the MaxL parameters from EXP30, in 2.5 hours of data surrounding the event at: t0-1.5 hours, t0-1., t0-0.5, t0+0.5, t0+1. For 3 of the 5 noise realisations, corresponding to t0-1 hour, t0+0.5 hours, and t0+1.0 hour we recover a damping time similar to the actual event, whereas for a third case, t0-0.5 hours, we obtain a damping time consistent at the 90\% credible interval (bottom panel of FIg.\ref{fig:21g_systematics}). L1-SNR goes down by more than 3 in some runs (maximum L1-SNR 12, minimum 9), indicative of how the noise variability is strongly affecting the recovered parameters. For some injections the mass ratio is biased, although final spin (most sensitive to mass ratio) is not affected much.  domega varies quite a lot among runs, instead dtau seems well behaved around zero. Effective frequency is a stable parameter (always well measured), while effective tau is much more sensitive to the noise configuration.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% modified GR signal: GR vs nonGR recovery comparison
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h!]
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
	\caption{\textcolor{red}{FINAL RESULT} Right panels: GW50914. Left panels: GW190521. \abhi{describe how we get final mass and spin}}
	\label{fig:gr_ngr_comparison}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\title{Black hole symphony orchestra: Spectroscopy using gravitational wave signals from binary black hole coalescences}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The no-hair conjecture in General Relativity states that the properties of a Kerr black hole (BH) are completely described by its mass and spin angular momentum. As a consequence, the complex quasi-normal-mode (QNM) frequencies of a binary black hole (BBH) ringdown can be uniquely determined by the mass and spin of the remnant object. Conversely, measurement of the QNM frequencies could be a independent test of the no-hair conjecture. This paper outlines a test of the no-hair conjecture by measuring the complex QNM frequencies of a BBH ringdown within the framework of, for the first time, a spinning inspiral-merger-ringdown waveform model, thereby using the entire signal power and removing dependency on the predicted or estimated start time of the proposed ringdown. We further demonstrate the robustness of the test against modified gravitational wave (GW) signals with a ringdown different from what GR predicts for Kerr BHs. The method was used to analyse the properties of the merger remnants for the events observed by LIGO-Virgo in the first half of their third observing run (O3a) in the latest LIGO-Virgo publication. In this paper, for the first time, we analyse the GW events from the first and second LIGO-Virgo observing runs and provide joint constraints with published results from O3a. We also analyse two events from the O3a list of events that were not considered for the initial analysis. Finally, the joint measurements of the fractional deviations in the frequency, $\df{220} = XX \pm$ and $\dtau{220} = YY \pm$ are the strongest constraints yet using this method. %Finally, we also present a investigation into possible systematic effects due to an incomplete understanding of the interferometric noise around the GW event on the results of this test.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

@@

Finally, we provide a simple demonstration of a test of the no-hair theorem using our model. As described in the introduction, any test of the no-hair theorem of BHs would need to involve independent measurements of (at least) two different QNMs. We use a simulated GW signal from the SXS catalog CITE corresponding a non-spinning BBH with a mass-ratio $q=6$ (SXS:BBH:0166), rescaled to a total mass of $M=84 \Mo$ (Table~\ref{tab:injection_values}). We choose an asymmetric system to increase the SNR in the higher modes. We also rescale the distance and orientation of the binary such that the total SNR of the signal in a network of three detectors, LIGO Hanford, Livingston and Virgo, is 75. Based on the LIGO-Virgo observations during O3a, such asymmetric and loud signals are no longer just a theoretical prediction but quite plausible at design sensitivities. Using this signal, we attempt to measure the QNM frequencies $(2,\pm 2)$ and $(3,\pm 3)$ modes together (Fig.~\ref{fig:nohair_sxs}). The SNR in other sub-dominant modes is too less for us to estimate them reliably.

@@

The LIGO-Virgo Collaboration recently released their testing GR catalogue containing results of this test for all events observed during O3a ~\cite{Abbott:2020jks}, which passed a threshold for the total (source-frame) mass $\geq 50 \Mo$ and SNRs in the pre- and post-merger regions $\geq 8$.The pre- and post-merger regions of the signal are identified as the power in the frequency content of the signal before and after the signal reaches peak amplitude, as determined by the maximum likelihood parameter estimation template. For the purpose of \cite{Abbott:2020jks}, we used a mass threshold and restricted ourselves to the highest-mass events which were expected to be most promising to study merger-ringdown. However, since our method relies on doing a parameter estimation on the entire inspiral-merger-ringdown signal, we require the SNR to be beyond a certain threshold throughout the signal for reliable parameter estimation of the initial and final quantities. In fact the SNR threshold alone should be sufficient for the analysis, and for this paper we have relaxed the mass threshold. This has added two events, GW190630$\_$185205 and GW190828$\_$063405, to the list of events considered in \cite{Abbott:2020jks} \abhi{Runs ongoing and looking promising}. Fig.~\ref{fig:o1o2_events} shows results from these two events along with GW190519$\_$153544, GW190521$\_$074359, GW190910$\_$112807.

For the first time, in this paper, we present results on the relevant events from LIGO-Virgo's first and second observing runs, alongside the above events. Applying the same thresholds as above, we find three additional events which could be included in the analysis: GW150914, GW170104, GW170729. The other high-mass events from O1-O2, GW170809, GW170814, GW170818 and GW170823 do not have an SNR of $8$ in the merger-ringdown signal. For the three relevant signals, GW150914, GW170104 and GW170729, we provide the posterior distributions in $(\df{220}, \dtau{220})$ in Fig.~\ref{fig:o1o2_events}. We also reconstruct the effective QNM parameters, $(\fngr{220}, \taungr{220})$ which are tabulated in Table~\ref{tab:qnm_o1o2_results}. \footnote{See Table IV of \cite{Abbott:2020jks} for a list of the SNR thresholds. The paper quotes them for the purpose of the IMR consistency test, but the same thresholds have been used for the $pSEOB$ test as well.} Among all the GW signals detected so far, GW150914 (solid curve in Fig.~\ref{fig:o1o2_events})is unique in its loudness, mass as well as the clarity of the signal, leading to the first, and to date, best attempt in measuring the QNM frequencies CITE.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% O1-O2 events
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
	\includegraphics[width=0.5\textwidth]{figures/rin_pseob_results.pdf}
	\caption{\textcolor{red}{PRELIMINARY RESULT} The 90\% credible levels of the posterior probability distribution of the fractional deviations in the frequency and damping time of the $(2,\pm 2)$ QNM, $\{\df{220},\dtau{220}\}$ and their corresponding one-dimensional marginalized posterior distributions, for events from O1, O2 and O3a passing a SNR threshold of $8$ in both the pre- and post-merger signal. The solid red curve marks the constraint the best single-event constraint, GW150914, whereas the contraints from the other events are indicated by the dash-dot curves. The joint constraints on $\{\df{220},\dtau{220}\}$ obtained using multiplying the likelihoods from individual events is given by the filled grey contours.\abhi{add curves from joint likelihood}\abhi{add a hierarchical curve if we want to include that analysis}}
	\label{fig:o1o2_events}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We show these joint likelihoods on $(\df{220}, \dtau{220})$, as well as the corresponding one-dimensional marginalised distributions as filled grey curves in Fig.~\ref{fig:o1o2_events}. These are the strongest constraints on possible deviations in the measurement of $(\df{220}, \dtau{220})$ to date using our method. \abhi{perhaps show 2 joint posteriors: only O3a and O3a+O1-O2 to explicitly show the tightening of the joint constraints by adding the O1-O2 events} \abhi{add text on the hierarchical analysis if we want to include that analysis}

\begin{table}
\begin{flushleft}
\begin{tabular}{llllllll}
\toprule
Event & \multicolumn{2}{c}{Redshifted} & \hphantom{X} & \multicolumn{2}{c}{Redshifted} \\
& \multicolumn{2}{c}{frequency [Hz]} & \hphantom{X} & \multicolumn{2}{c}{damping time [ms]} \\[0.075cm]
\hline
& IMR  & pSEOB & \hphantom{X} & IMR  & pSEOB \\
\hline

@@

GWGW190630$\_$185205 &
$-$ &
$-$ &
\hphantom{X} &
$-$ &
$-$
\\[0.075cm]

GW190828$\_$063405,170729 &
$-$ &
$-$ &
\hphantom{X} &
$-$ &
$-$
\\[0.075cm]
\hline
\bottomrule
\end{tabular}
\caption{\textcolor{red}{NOT COMPLETE}}
\label{tab:qnm_o1o2_results}
\end{flushleft}
\end{table}

@@

In Section~\ref{sec:method}, we mentioned that the expression of the Bayesian likelihood function outlined in Eqs.~\ref{eq:likelihood} and \ref{eq:nwip} is only valid if the interferometric noise can be described as a stationary Gaussian process. LIGO-Virgo noise, however, frequently has non-stationary and/or non-Gaussian features, for example glitches, which can affect parameter inferences unless appropriately accounted for. Here we demonstrate with an example of a GW190521-like simulated signal, systematic biases likely originating from an incomplete understanding of the noise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.5\textwidth]{figures/S190521g_swinjs.png}
	\caption{\textcolor{red}{FINAL RESULT} 90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220}$ from simulations of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines). The GR prediction for the frequency and damping time is indicated by the black cross. While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not. For comparison, we also plot the 90 \% credible level for the actual event, GW190521.}
	\label{fig:21g_systematics}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We use as our underlying GR signal, an NR waveform (using the waveform model \texttt{NRSur7dq4}) with parameters similar to the actual event GW190521 (as reported in Table I of \cite{Abbott:2020tfl}). The predictions of the frequency and damping time for the GR signal we choose are indicated by the black cross in Fig.~\ref{fig:21g_systematics}, and for comparison, the results on the actual signal are shown with a black solid curve. It would appear that while the measurement of the frequency is consistent with the prediction, we overestimate the damping time.

The underlying NR signal is expected to be precessing, and since the $pSEOB$ model is built on an aligned-spin GR model, a lack of precession could bias measurements. We explore effects of possible waveform systematics by injecting the signal is coloured Gaussian noise. In this case, since the understanding of the noise realisations is complete, any measurement biases could only arise from incomplete understanding of the underlying signal. We find (grey curves in Fig.\ref{fig:21g_systematics}) our results to be consistent with the prediction thus ruling out a lack of precession to be a likely cause for the bias in the damping time measurement of the actual signal.

We subsequently study the effects of possible noise systematics by injecting the same \texttt{NRSur7dq4} GW signal in different realisations of actual interferometric noise around the real event GW190521. Since the PSDs of the GW detectors are expected to vary over longer durations of time, we select 5 different noise realisations over a segment of 2.5 hours of coincident data in both the LIGO detectors centred at the time of the actual event. The noise properties in this chunk of data, and consequently for all 5 simulated signals, is expected to be the closest to that for the actual event. The results are indicated by pink curves in Fig.~\ref{fig:21g_systematics}. For 3 of the 5 noise realisations, corresponding to $t_0-1$ hour, $t_0+0.5$ hours, and $t_0+1$ hour we recover a damping time similar to the actual event, where $t_0$ is the GPS time of the actual event. For the other two noise realisations, we estimate the consistent damping time but an off-set frequency, while the fifth noise realisation is consistent with both predictions. The SNR in the L1 Livingston detector goes down by more than 3 in some runs, indicative of how a variation in the noise strongly affects our ability to infer parameters. This also seems to indicate that a bias in the measurements of the damping time for the actual event can be unaccounted noise systematics.

\section{Correlations between GR and non-GR parameters}\label{sec:correlations}
\abhi{Do we want a separate appendix to discuss Fig.~\ref{fig:gr_ngr_comparison}? Or is the reference in the main text currently, sufficient?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% modified GR signal: GR vs nonGR recovery comparison
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h!]
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_m1m2.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_m1m2.png}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_a1za2z.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_a1za2z.png}	
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_fgrtaugr.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_fgrtaugr.png}
	\includegraphics[width=0.5\textwidth]{figures/GW150914_simulated_signal_0p5_gr_ngr_Mfaf.png}\includegraphics[width=0.5\textwidth]{figures/GW190521_simulated_signal_0p5_gr_ngr_Mfaf.png}
	\caption{\textcolor{red}{FINAL RESULT} Comparison of the recovered parameters when the underlying signal is assumed to be a GR signal or a modified GR signal. In both cases, the actual underlying signal is a modified GR signal with parameters similar to GW150914 (left panels) and GW190521 (right panels) respectively. The initial parameters are given in Table~\ref{tab:injection_values}, with the QNM parameters defined by $\df{220} = \dtau{220} = 0.5$. For the GW150914 (GW190521) contours, the $SEOB$ and $pSEOB$ recoveries are indicated by blue (red) and pink (grey) curves respectively. The panels (from top to bottom) show the recoveries in (detector-frame) initial masses (first row), z-components of dimensionless initial spins (second row), GR predictions of frequency and damping time (third row) and the remnant mass and spin predictions ($M_f, a_f$) from the frequency and damping time (obtained by inverting the Berti fits) CITE}
	\label{fig:gr_ngr_comparison}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
